Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-03-31 src/tex/ms.tex
GPT pass

Similarly, using the same procedures, distributions of mismatches calculated
using {\zdethp} noise spectrum show better improvement than the weighted
mismatch. The shape of the distribution is similar to Fig.~\ref{fig:q148}. This
effect is expected since the IMRPhenomD model was originally constructed and
fitted using the {\zdethp} weighted mismatch. Thus, it should be a model that
fits closely to the NR waveforms with the influence of {\zdethp} noise spectrum
instead of the constant spectrum.

With the success of improving waveforms, we increase the number of training
waveforms for optimization. Taking additional waveforms listed in
Tab.~\ref{tab:q1248}, we obtain a new set of coefficients. We see in Fig.
\ref{fig:q148_q1248_compare}, new waveforms produced only have a very small
improvement. The high mismatch tail of the optimized distribution remains
similar in length and endpoint as the original distribution, meaning that they
cannot be improved using our procedure. Likewise, using additional waveforms to
optimize loss function with {\zdethp} spectrum shows the same result, where the
new distribution barely shows any improvement.

@@

Given the ansatz used in the waveform model is unlikely to be fully compatible
with NR, and the optimization procedure is done over a distribution of waveforms
with different source parameters, it is conceivable that there are some
trade-off in accuracy of the waveform models between different part of the
parameter space. If this is the reason why the high mismatch tail is not
improving during the joint-optimization, separating the parameter space into
smaller subspace should help alleviate this issue. On the other hand, if the
ansatz does not have the right parameterized form to capture the behavior of the
NR waveforms as a function of the intrinsic parameters, the result should be
always biased, and we should not expect any improvement even if we separate the
parameter space into smaller space during training.

>>>>

Applying the same methods, we observe that the distributions of mismatches
calculated using the {\zdethp} noise spectrum exhibit superior improvement
compared to the weighted mismatch. The shape of the distribution is similar to
that shown in Fig. \ref{fig:q148}. This result is expected, as the IMRPhenomD
model was initially constructed and fitted using the {\zdethp} weighted
mismatch. Consequently, the model is anticipated to closely fit the NR waveforms
while incorporating the influence of the {\zdethp} noise spectrum, rather than a
constant spectrum.

Motivated by the successful improvement of the waveforms, we expand the training
dataset to optimize additional waveforms listed in Tab. \ref{tab:q1248}. The new
set of coefficients generated from this optimization process yields only
marginal improvements in the newly produced waveforms, as seen in Fig.
\ref{fig:q148_q1248_compare}. The high mismatch tail of the optimized
distribution remains comparable in length and endpoint to the original
distribution, indicating that our procedure is incapable of improving these
waveforms. Similarly, utilizing the {\zdethp} spectrum to optimize the loss
function with additional waveforms leads to minimal improvement in the resulting
distribution.

@@

Given that the waveform model's ansatz may not be entirely compatible with NR,
and the optimization procedure is carried out over a distribution of waveforms
with varying source parameters, it is conceivable that some trade-offs in
accuracy exist between different parts of the parameter space. If this is the
cause of the high mismatch tail's failure to improve during joint-optimization,
segmenting the parameter space into smaller subspaces should alleviate this
problem. On the other hand, if the ansatz lacks the correct parameterized form
to capture the NR waveforms' behavior as a function of the intrinsic parameters,
the results will always be biased, and we should not expect any improvement,
even if we segment the parameter space during training.
